\NAME: A framework for \\ Efficient Intrusion Detection\\ in the Internet of Things

### 2014-10-22 paper.tex
completed draft text for architecture evaluation

Figure \ref{fig:architecture} shows the architecture of the implementation.

@@

@@

\subsection{Evaluation}

>>>>

Figure \ref{fig:architecture} shows the architecture of the implementation. It
illustrates the generation of the DSL into compilable code, using the Nodes
domain information, a platform and language description and the native software
library. The applied grayscale indicates the components' platform dependency:
the DSL is platform and language independent and deals with subsystems, such as
the network, in an abstract way. The Nodes domain implements some of these
abstracted subsystems, but still in a platform and language independent way.
The platform and language descriptions define the actual target platform and
language and convert the abstract constructions in actually supported code. The
software library is written in native code targeting the platform and language.
Finally, the code and the image are artifacts of the automated generation and
compilation process. They aren't a product of manual work and therefore aren't
directly dependent on the platform.

@@

This hierarchy is important from a development effort point of view. The level
of dependency on the platform also dictates the level of effort to implement
changes to the platform. For example: changing the language will require a
complete rewrite of the software library and a partial rewrite of the language
description of the generator. Although this is a one-time effort, it is
important in relation to the scalability of the framework.

@@

\subsection{Experimental Results}
